---
title: "Welcome."
---

```{r echo = FALSE, message = FALSE}
if (!require("badger")){
  install.packages("badger")
}
library("badger")
if (!require("stringr")){
  install.packages("stringr")
}
library("stringr")
if (!require("ggplot2")){
  install.package("ggplot2")
}
library(ggplot2)
if (!require("ggiraph")){
  install.package("ggiraph")
}
library(ggiraph)
```

`r badge_last_commit("xiangjiexue/xiangjiexue.github.io")`
`r badge_lifecycle("experimental", "orange")`

My homepage is currently under initial development.

```{r echo = FALSE}
filename = list.files(recursive = TRUE)
filesize = sapply(filename, function(fn){file.info(fn)$size / 1024})
filework = rep(FALSE, length(filename))
filework[grep("*pdf", filename)] = TRUE
filework[grep("*Rmd", filename)] = TRUE
filework[grep("*yml", filename)] = TRUE
filework[grep("*bib", filename)] = TRUE
filework2 = ifelse(filework, "Human work", "Computer Intelligence")
df = data.frame(filename = filename, filesize = filesize, filework = filework2)
gg_point = ggplot(df, aes(x = "", y = filesize, fill = filework)) +
  geom_bar_interactive(width = 1, stat = "identity", tooltip = paste(filename, "has size", round(filesize, 1), "kB"), data_id = filesize) +
  labs(title = "Human work vs compute intelligence", fill = NULL) + xlab(NULL) + 
  ylab("File size (kB)") + 
  theme(legend.position = "bottom") +
  scale_y_continuous(sec.axis = sec_axis(~ . / sum(filesize), name = "Percentage"))
girafe(ggobj = gg_point)
```

This is a good example on how computer programs change our life: only small amount of code (`r sum(filesize[filework]) / sum(filesize) * 100`%) is written by me and the rest is taken care of by various software packages.

**The latest blog from me:**

***
<!-- used regex to get the latest blog from ./blog.html -->

`r {singleString <- paste(readLines("blog.Rmd"), collapse="\n"); stringr::str_extract_all(singleString, "(?<=\\*\\*\\*\\n)##([\\s\\S]*?)\\n\\n")[[1]][1];}`

***
This website is built in R using Rstudio, and
hosted by github_pages. Special thanks to the following R 
packages in building this website:

* rmarkdown for building website `r badge_cran_release("rmarkdown", "orange")` 
`r badge_dependencies("rmarkdown")` `r badge_cran_checks("rmarkdown")`

* badger for creating badges `r badge_cran_release("badger", "orange")` 
`r badge_dependencies("badger")` `r badge_cran_checks("badger")`

* stringr for implementing the latest blog session on the homepage `r badge_cran_release("stringr", "orange")` 
`r badge_dependencies("stringr")` `r badge_cran_checks("stringr")`

* ggplot2 for plotting `r badge_cran_release("ggplot2", "orange")` 
`r badge_dependencies("ggplot2")` `r badge_cran_checks("ggplot2")`

* ggiraph for generating interactive plots using ggplot2 `r badge_cran_release("ggiraph", "orange")` 
`r badge_dependencies("ggiraph")` `r badge_cran_checks("ggiraph")`

See build information [here](./buildinfo.html).
