---
title: "List of all references"
author: "Xiangjie Xue"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
# bibliography: Refs.bib
# nocite: '@*'
---

```{r echo = FALSE, message = FALSE}
if (!require(jsonlite)){
  install.packages("jsonlite")
}
library(jsonlite)
if (!require(dplyr)){
  install.packages("dplyr")
}
library(dplyr)
if (!require(DT)){
  install.packages("DT")
}
library(DT)
```

The following table only shows the first two authors. This table is for personal
use only.
```{r echo = FALSE}
rawdata = read_json("./Refs.json")
rawdata1 = lapply(rawdata, function(x){
  temp = unlist(x)
  temp2 = matrix(temp, nrow = 1)
  colnames(temp2) = names(temp)
  data.frame(temp2)
})
df = Reduce(bind_rows, rawdata1)
df = select(df, "id", "issued.date.parts", "title", "type", "author.family",
            "author.family.1", "author.family.2")
colnames(df) = c("id", "year", "title", "type", "author1.family", 
                 "author2.family", "author3.family")
datatable(df, filter = list(position = 'top', clear = TRUE), rownames = FALSE)
```

This table is generated using
```{r eval = FALSE}
/Applications/RStudio.app/Contents/MacOS/pandoc/pandoc-citeproc --bib2json Refs.bib > Refs.json
```

### Related R packages

* jsonlite `r badge_cran_release("jsonlite", "orange")` 
`r badge_dependencies("jsonlite")` `r badge_cran_checks("jsonlite")`

* dplyr `r badge_cran_release("dplyr", "orange")` 
`r badge_dependencies("dplyr")` `r badge_cran_checks("dplyr")`

* DT `r badge_cran_release("DT", "orange")` 
`r badge_dependencies("DT")` `r badge_cran_checks("DT")`
