---
title: "R packages"
bibliography: Refs.bib
---

```{r echo = FALSE, message = FALSE}
if (!require("badger")){
  install.packages("badger")
}
library("badger")

if (!require("devtools")){
  install.packages("devtools")
}
library("devtools")
```

This page gives some details about the R package that I have written.

***
**Something about R**


R is a language and environment for statistical computing and graphics. It is a
GNU project which is similar to the S language and environment which was 
developed at Bell Laboratories (formerly AT&T, now Lucent Technologies) by John 
Chambers and colleagues.

R provides a wide variety of statistical (linear and nonlinear modelling, 
classical statistical tests, time-series analysis, classification, clustering, 
...) and graphical techniques, and is highly extensible.

More details can be found [HERE](https://r-project.org/)

***

## npfixedcompR

`r badge_last_commit("xiangjiexue/npfixedcompR")` 
`r badge_custom("on CRAN", "no", "red")`

During [my PhD study](./phdthesis.html), I have developed different approaches
to estimating a mixing distribution (or mixtures) non-parametrically and 
implemented these in R. The source code can be found on 
[this Github repo](https://github.com/xiangjiexue/npfixedcompR) and can be
installed using the devtools package.

```{r, eval = FALSE}
devtools::install_github("xiangjiexue/npfixedcompR")
```

***
**non-parametric mixtures**

According to @RN104, The non-parametric mixture model assumes that the 
distribution of all underlying incidental parameters is treated as completely 
unspecified as to whether it is discrete, continuous or in any particular family
of distributions.

***

We use the $z$-values of the prostate data mentioned in @RN255 as an example.
There are 6033 observations and we are interested in investigating the
proportion of null effects ($z$-statistic is 0) and the non-null effects. With 
no assumption of the underlying structure of the null effects, non-parametric
method should be used. With this R package, we can estimate the distribution
of the non-null effect given the null proportion. In this case, we assume the
component density is normal and use non-parametric maximum likelihood to find
the mixing distribution.

```{r, echo = FALSE, message = FALSE}
library(npfixedcompR)
library(nspmix)
load(url("http://statweb.stanford.edu/~ckirby/brad/LSI/datasets-and-programs/data/prostz.RData"))
hist(prostz, probability = TRUE, breaks = 100, main = expression(paste("Density Estimates for various ", pi[0])), ylab = "Density", xlab = NULL, ylim = c(0, 0.45))
col1 = rainbow(6)
x = makeobject(prostz)
plot(computemixdist(x), add = TRUE, col = col1[1], col1 = col1[1])
x = makeobject(prostz, pi0 = 0.2)
plot(computemixdist(x), add = TRUE, col = col1[2], col1 = col1[2])
x = makeobject(prostz, pi0 = 0.4)
plot(computemixdist(x), add = TRUE, col = col1[3], col1 = col1[3])
x = makeobject(prostz, pi0 = 0.6)
plot(computemixdist(x), add = TRUE, col = col1[4], col1 = col1[4])
x = makeobject(prostz, pi0 = 0.8)
plot(computemixdist(x), add = TRUE, col = col1[5], col1 = col1[5])
legend("topright", legend = expression(pi[0] == 0, pi[0] == 0.2, pi[0] == 0.4, pi[0] == 0.6, pi[0] == 0.8), col = col1[1:5], bg = "white", lty = 1)
```

It is also possible to estimate the null proportion using a threshold function 
(analogue to variable selection). Taking AIC as an example

```{r, echo = FALSE, message = FALSE}
x$estpi0()
hist(prostz, probability = TRUE, breaks = 100, main = expression(paste("Density Estimates for various ", pi[0])), ylab = "Density", xlab = NULL, ylim = c(0, 0.45))
plot(x$result, add = TRUE)
print("Estimated pi0")
x$result$mix$pr[x$result$mix$pt == 0]
```

***
R packages used on this page

* lsei `r badge_cran_release("lsei", "orange")` 
`r badge_dependencies("lsei")` `r badge_cran_checks("lsei")`

* nspmix `r badge_cran_release("nspmix", "orange")` 
`r badge_dependencies("nspmix")` `r badge_cran_checks("nspmix")`

* devtools `r badge_cran_release("devtools", "orange")` 
`r badge_dependencies("devtools")` `r badge_cran_checks("devtools")`

### References
